PAQ for parenting observational study

### 2017-03-23 paq/parenting_obs_paq.Rmd
lex diversity script

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(rjson)
library(stringr)
library(forcats)
library(tibble)

@@

ggplot(ms, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

>>>>

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(rjson)
library(stringr)
library(forcats)
library(tibble)
library(lme4)

@@

ggplot(ms, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

da <- dq %>%
  group_by(sid, parent_ed, category) %>%
  filter(!is.na(parent_ed))%>%
  multi_boot_standard(col = "rating", na.rm = TRUE)

da$parent_ed <- as.numeric(da$parent_ed)
```
Stats
```{r eval = FALSE}
mod <- lmer(mean ~ parent_ed *  category +
                           (1 | sid), 
                         data = da)
summary(mod)
```
